Large-Scale Marine Protected Areas in the World's Largest Tuna Fishery

### 2019-03-05 docs/PIPA_Palau030319.tex
Added updated figures and new MS

\begin{abstract}
The Parties to the Nauru Agreement (PNA) is a system for managing the world’s largest skipjack tuna fishery, covering an area of 14.6 million km\textsuperscript{2} in the Pacific Ocean. The fishery in the region operates under a Vessel-Day Scheme (VDS), which sells access rights that allow vessels to fish in PNA waters. In 2015, PNA member Kiribati implemented one of the world's largest conservation areas: The Phoenix Islands Protected Area (PIPA, 397,447 km\textsuperscript{2}), effectively excluding all tuna purse seining activities. Such an intervention is likely to have effects on vessel spatial distribution and behavior, as well as induce costs (due to the reduction in fishable area) to Kiribati. We use identification of fishing activity via Automatic Identification Systems and causal inference techniques to evaluate the effect of PIPA on vessel distribution, behavior, and costs to Kiribati and the PNA. We find a crowding effect within PNA waters after the implementation of the protected area. Vessels continue to fish with similar intensity after the implementation. In the first year of the closure, there is no drop in total fishing effort within Kiribati's EEZ and a reported increase in revenue from access rights sold. However, from 2016 onward there is a noticeable drop in fishing effort within Kiribati and a reported drop in VDS revenue. At the same time, fishing effort increases in other parts of the PNA. This redistribution of fishing effort eventually results in a reduction of 2,310 vessel-days in Kiribati, which represents a loss of \$27.7 million USD; similar estimates are obtained when looking at country-level license fees revenues directly (\$30.5 million USD). We use our results to inform predictions of the impacts of a proposed Large-Scale Marine Protected Area (LSMPA) in Palau (another PNA member) and estimate potential losses to range from \$2.5 to \$11 million annually. PNA members who indirectly benefit from MPAs should consider mechanisms that reward such conservation actions.
\end{abstract}

>>>>

\begin{abstract}
The Parties to the Nauru Agreement (PNA) is a system for managing the world’s largest skipjack tuna fishery, covering an area of 14.6 million km\textsuperscript{2} in the Pacific Ocean. The fishery in the region operates under a Vessel-Day Scheme (VDS), which sells access rights that allow vessels to fish in PNA waters. In 2015, PNA member Kiribati implemented one of the world's largest conservation areas: The Phoenix Islands Protected Area (PIPA, 397,447 km\textsuperscript{2}), effectively excluding all tuna purse seining activities. Such an intervention is likely to have effects on vessel spatial distribution and behavior, as well as induce costs (due to the reduction in fishable area) to Kiribati. We use identification of fishing activity via Automatic Identification Systems and causal inference techniques to evaluate the effect of PIPA on vessel distribution, behavior, and costs to Kiribati and the PNA. We find a crowding effect within PNA waters after the implementation of the protected area. Vessels continue to fish with similar intensity after the implementation. In the first year of the closure, there is no drop in total fishing effort within Kiribati's EEZ and a reported increase in revenue from access rights sold. However, from 2016 onward there is a noticeable drop in fishing effort within Kiribati and a reported drop in VDS revenue. At the same time, fishing effort increases in other parts of the PNA. This redistribution of fishing effort eventually results in a reduction of 5,195 vessel-days in Kiribati, which represents a loss of \$46.7 million USD; similar estimates are obtained when looking at country-level license fees revenues directly (\$30.5 million USD).  We use our results to inform predictions of the impacts of a proposed Large-Scale Marine Protected Area (LSMPA) in Palau (another PNA member) and estimate potential losses to range from \$2.5 to \$11 million annually. PNA members who indirectly benefit from MPAs should consider mechanisms that reward such conservation actions.
\end{abstract}

### 2019-03-05 docs/tab/sp_corr.tex
Added updated figures and new MS

\begin{table}[!htbp] \centering 
  \caption{\label{tab:sp_corr}Coefficient estimates for a third-polinomial fit to the measures of crowding. The first column shows coefficients for the number of cells with treated and control vessels during the same month. The second column shows coefficients for the spatial correlation for presence / absence of treated and control vessels. The explanatory variable is the number of months before implementation of PIPA. Numbers in parentheses are heteroskedastic-robust standard errors.} 
  \label{} 
\footnotesize 
\begin{tabular}{@{\extracolsep{1pt}}lcc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
\\[-1.8ex] & (1) & (2)\\ 
\hline \\[-1.8ex] 
 Constant & 59.999$^{***}$ (15.581) & 0.370$^{***}$ (0.062) \\ 
  $M$ & 3.014$^{***}$ (0.967) & 0.009$^{**}$ (0.003) \\ 
  $M^2$ & 0.010 (0.027) & $-$0.0001 (0.0001) \\ 
  $M^3$ & $-$0.002$^{***}$ (0.001) & $-$0.00001$^{***}$ (0.00000) \\ 
  $M^4$ & 0.00000 (0.00002) & 0.00000 (0.00000) \\ 
  $\sigma_1$ & 22.342 (19.528) & 0.057 (0.076) \\ 
  $\sigma_2$ & 5.413 (18.860) & $-$0.015 (0.035) \\ 
 \hline \\[-1.8ex] 
Month FE & Yes & Yes \\ 
Flag FE & Yes & Yes \\ 
Observations & 83 & 84 \\ 
R$^{2}$ & 0.791 & 0.709 \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{2}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{table}

>>>>

\begin{table}[!htbp] \centering 
  \caption{\label{tab:sp_corr}Coefficient estimates for a third-polinomial fit to the measures of crowding. The first column shows coefficients for the number of cells with treated and control vessels during the same month. The second column shows coefficients for the spatial correlation for presence / absence of treated and control vessels. The explanatory variable is the number of months before implementation of PIPA. Numbers in parentheses are heteroskedastic-robust standard errors.} 
  \label{} 
\footnotesize 
\begin{tabular}{@{\extracolsep{1pt}}lcccccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6) & (7) & (8)\\ 
\hline \\[-1.8ex] 
 Constant & 78.040$^{***}$ & 84.639$^{***}$ & 60.962$^{***}$ & 66.725$^{***}$ & 0.412$^{***}$ & 0.417$^{***}$ & 0.370$^{***}$ & 0.377$^{***}$ \\ 
  & (5.438) & (8.990) & (15.598) & (15.988) & (0.014) & (0.032) & (0.062) & (0.066) \\ 
  & & & & & & & & \\ 
 M & 3.943$^{***}$ & 4.065$^{***}$ & 3.066$^{***}$ & 3.139$^{***}$ & 0.010$^{***}$ & 0.010$^{***}$ & 0.009$^{**}$ & 0.009$^{**}$ \\ 
  & (0.302) & (0.348) & (0.966) & (1.040) & (0.001) & (0.001) & (0.003) & (0.004) \\ 
  & & & & & & & & \\ 
 M $^2$ & $-$0.005 & $-$0.021 & 0.008 & $-$0.008 & $-$0.0001$^{***}$ & $-$0.0001 & $-$0.0001 & $-$0.0001 \\ 
  & (0.019) & (0.026) & (0.027) & (0.030) & (0.00004) & (0.0001) & (0.0001) & (0.0001) \\ 
  & & & & & & & & \\ 
 M $^3$ & $-$0.002$^{***}$ & $-$0.002$^{***}$ & $-$0.002$^{***}$ & $-$0.002$^{***}$ & $-$0.00001$^{***}$ & $-$0.00001$^{***}$ & $-$0.00001$^{***}$ & $-$0.00001$^{***}$ \\ 
  & (0.0003) & (0.0003) & (0.001) & (0.001) & (0.00000) & (0.00000) & (0.00000) & (0.00000) \\ 
  & & & & & & & & \\ 
 M $^4$ & 0.00001 & 0.00002 & 0.00000 & 0.00001 & 0.00000$^{***}$ & 0.00000$^{**}$ & 0.00000 & 0.00000 \\ 
  & (0.00001) & (0.00002) & (0.00002) & (0.00002) & (0.00000) & (0.00000) & (0.00000) & (0.00000) \\ 
  & & & & & & & & \\ 
 NINO4 &  & $-$8.095 &  & $-$10.395 &  & $-$0.006 &  & $-$0.014 \\ 
  &  & (8.287) &  & (9.481) &  & (0.029) &  & (0.031) \\ 
  & & & & & & & & \\ 
 $\sigma_1$ &  &  & 21.318 & 25.102 &  &  & 0.057 & 0.062 \\ 
  &  &  & (19.493) & (22.486) &  &  & (0.076) & (0.080) \\ 
  & & & & & & & & \\ 
 $\sigma_2$ &  &  & 5.299 & 3.194 &  &  & $-$0.015 & $-$0.018 \\ 
  &  &  & (18.874) & (18.670) &  &  & (0.035) & (0.035) \\ 
  & & & & & & & & \\ 
\hline \\[-1.8ex] 
NINO4 & No & Yes & No & Yes & No & Yes & No & Yes \\ 
Satellites & No & No & Yes & Yes &  &  &  &  \\ 
Observations & 84 & 84 & 84 & 84 & 84 & 84 & 84 & 84 \\ 
R$^{2}$ & 0.791 & 0.793 & 0.795 & 0.798 & 0.703 & 0.704 & 0.709 & 0.710 \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{8}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{table}
